Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-11 paper/main.tex
minor changes to discussion of group

% study goal
The goal of this study was to investigate if cues about the spatial layout
embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA that was define by using a visual localizer experiment
within the same subjects \citep{sengupta2016extension}.
% what we did We
annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used conceptualized
stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from the visual localizer.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.\todo{``localization'' performance}
% NeuroVault
Unthreholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
private collection}

@@

\todo[inline]{paragraphs start with 1-2 sentences that set up the question
that the paragraph answers; e.g. ``To verify that\dots''}

\todo[inline]{middle of paragraph presents data \& logic that pertain the
question}

\todo[inline]{paragraph ends with a concluding / logical statement}

@@

\todo[inline]{which contrast yielded NO clusters?}

\todo[inline]{I consider tables of significant clusters in PPA for all contrasts
as overkill. Maybe in ``supporting material'' or reference to dataset? all sign.
clusters of all contrasts are in the comments}

@@

\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
wichtige Hinweise geben}

@@

\todo[inline]{SE: RSC etc: Irgendwie waren die bis zu Diskussion eher ein
afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
schon mehr bringen; COH: afterthought, for sure; It was highly probable that RSC
would show up but it wasn't aim of the study (had no ROIs for it anyway); imo
this is an issue of story telling vs. hypotheses after results}

\todo[inline]{structure is as follows: correlation of
regressors; AO group; AV group; robustness AO + AV; anterior vs posterior PPA;
other clusters significant across contrasts (= retrosplenial cortex and
occipital place area)}

@@

% previous studies: visual
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to
pictures of faces or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal}) whereas one study using spoken sentences reported
mixed results \citep{aziz2008modulation}.
% we use similar statistical models but with naturalistic stimuli
Here, we use statistical models that are similar to previous studies that used
small sets of experimentally controlled stimuli to investigate hemodynamic brain
responses during two naturalistic stimuli.
% more than just one contrast
We computed varying GLM contrasts that differed in the contrasted categories and
the amount of available data to test the robustness of our findings in both
stimuli.
% comparison to localizer experiment
We compare results of the primary contrast of each stimulus on the level of
individual subjects to results that we gained from a dedicated visual localizer
paradigm done with the same subjects \citep{sengupta2016extension}.
% summary of results main finding
Results of our whole-brain analyses suggest that the perception of verbal
``spatial information'' embedded in an auditory narrative contrasted with
``non-spatial information'' is correlated with increased activation in the
anterior PPA of both hemispheres.
% to do
\todo[inline]{this is just the main finding; other possible ``honourable''
mentions like robustness of results, AV stimulus, individual results?}

@@

\todo[inline]{Following paragraph could pasted into method section to save space
here; a short interpretation is given there already; so methods/ results/
discussion are not absolutely separated there already}
% stimuli not designed for research purposes
Both naturalistic stimuli were not designed to be used in a BOLD fMRI experiment
but to entertain their audiences.
% why correlation matrix  was created
Thus, we first tested for correlation of regressors (s. \ref{fig:reg-corr}) that
are based on the annotated stimulus features because a high degree of shared
variance lowers detection power
% results of computing feature correlation
Results show no to minor correlations of regressors across all stimulus
segments.
% encouraged by that we build contrasts (statement)
Thus we felt encouraged to create traditional/canonical voxel-wise GLMs that
modeled and contrasted hemodynamic activity similarly to previous studies that
used simplified stimuli.

@@

% AO stimulus
Group results of the AO stimulus' primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap taken from
\citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
model hemodynamic responses but modeled from on- to offset of single words that
cue the listener about the movie's missing visual content.
% conclusion
Our group results suggest that auditory spatial information does not just
modulate activity in the PPA (depending on other factors like familiarity; s.
\citep{aziz2008modulation}) but correlates with bilaterally increased
activation.\todo{``modulate'' suggests causation}

% Previous studies used tasks
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but epstein1998
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a (perceptual) judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Our paradigm still differs from \citep{epstein1998ppa} because the relevant
stimulus features were incidentally embedded in a continuous stream of auditory
information.
% conclusion
The embeddedness prevents participants from making assumptions about the
investigated perceptual process by just being exposed to the paradigm and thus
mimics experiencing the world outside the lab more closely.
% concluding statement: kinda automatic process
The lack of a task further suggests that verbal spatial information is processed
in the PPA in an automatic fashion and does not necessarily rely on deliberately
paying attention to spatial information.

\todo[inline]{following: how to frame it (better) that AV merely serves as
conceptual control?; imo discussion of AV should be short anyway}
% AV stimulus
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
overlap) with group ROI?}
% confound of higher perception
This larger extension, especially into the primary visual cortex, can be
attributed to the fact that we averaged the content of individual frames after a
cut and did not control for confounding features like depicted faces or
objects,and low-level visual features.
% cross-modal control purpose?
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
results?}

@@

% why we did a couple of contrasts
For both stimuli we created additional contrasts that varied the amount of
events available for the analysis and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show significant
bilateral clusters in the anterior part of the group PPA overlap.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but extending into more posterior brain regions.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust across contrasts and do not depend on the design of one specific
contrasts.

% but
Nevertheless, results also suggest that localization performance depends on the
amount of available data and how well the feature space is modeled.
% example
For example, contrast 8 of the AO stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a stimulus to be chosen may provide and how homogeneous the events to be
averaged might be.

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements[, or
memory].\todo{which kind of memory}
% AO: auditory cortices
For example in the AO results, contrasts that compare (among other categories)
verbal cues about the change of a setting (\texttt{se\_new} > \texttt{se\_old})
to categories that do not cue a change of a setting (contrasts 2, 3, 6, 7) show
significant clusters in (primary and secondary) auditory cortices.\todo{``poor
job of nuisance regressors?}
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.\todo{ouf\dots}
% possible reason
This could be attributed to a possible change of the soundscape and/or increased
volume when the narrative switches to a new setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

% intro
Results of the AO contrasts consistently yielded significant clusters spatially
constrained to the anterior part of the PPA group overlap (and to the anterior
part of significant clusters of the AV contrasts).
% PPA might have submodules
Previous studies provide evidence that the posterior PPA (pPPA) and anterior PPA
(aPPA) show differences in both functional connectivity profiles and in
response to low- and high-level visual features.

% posterior connectivity
The pPPA is more strongly functionally connected to the occipital visual cortex
\citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% functionality
The pPPA is functionally more responsive than aPPA to low-level features of
scenes or (abstract) objects \citep{baldassano2013differential,
nasr2014thinking, rajimehr2011parahippocampal}.

% anterior
The anterior PPA is more strongly functionally connected to portions of the
default mode network, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe \citep{baldassano2013differential, baldassano2016two}
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).

\todo[inline]{the mother of total confusion: in Aminoff (2007, 2013): anterior
    PPA = spatial associations, region anterior to PPA = non-spatial
    associations; but in Aminoff (2015): posterior PPA = spatial associations
    and anterior PPA = non-spatial associations; hence: complete bullshit;
ignore Aminoff (2015) due to various reasons}

@@

\todo[inline]{check location in primary contrast and in overlap of contrasts}

\todo[inline]{numbers of contrast in AO \& AV that show sign. clusters in
LOC}

\todo[inline]{e.g.
Nakamura (2000). Functional delineation of the human occipito-temporal areas;
Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene Perception;
Dilks, Kanwisher (2013). The Occipital Place Area Is Causally and Selectively Involved in Scene Perception;
Grill-Spector (2003). The neural basis of object perception;
Nasr (2011). Scene-selective cortical regions in human and nonhuman primates;
Hasson (2003). Large-scale mirror-symmetry organization;
MacEvoy and Epstein (2007). Position selectivity in scene- and object-responsive\dots;
Dilks (2011). Mirror-image sensitivity and invariance in object \& scene processing}

@@

\todo[inline]{``problem'': if discussion of anterior vs. posterior PPA above
turns out that anterior PPA is a submodul of the PPA we do not localize a
``visual area'' with an auditory stimulus}

>>>>

% study goal
The goal of this study was to investigate if cues about the spatial layout
embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA that was define by using a visual localizer experiment
within the same subjects \citep{sengupta2016extension}.
% what we did We
annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used conceptualized
stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from the visual localizer.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.\todo{``localization'' performance}
% NeuroVault
Unthreholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts for both naturalistic stimuli can be found
at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
private collection}

@@

@@

\todo[inline]{tables of significant clusters all contrasts = overkill!? Link to NeuoVault is added; sign. clusters of all contrasts are listed in the comments}

@@

\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
wichtige Hinweise geben; COH: imo discussing that will let the paper get way out
of hand}

@@

\todo[inline]{SE: RSC etc: Irgendwie waren die bis zu Diskussion eher ein
afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
schon mehr bringen; COH: afterthought, for sure; It was highly probable that RSC
would show up but it wasn't aim of the study (had no ROIs for it anyway); imo
this is an issue of ``nice story telling'' vs. HARKing}

@@

% previous studies: visual
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to
pictures of faces or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal}) whereas one study using spoken sentences reported
mixed results \citep{aziz2008modulation}.
% we use similar statistical models but with naturalistic stimuli
Similarly to previous studies that used small sets of experimentally controlled
stimuli, we also used GLMs to investigate hemodynamic brain activity during two
naturalistic stimuli.
% more than just one contrast
For both naturalistic stimuli, we computed several $t$-contrasts that differed
in the contrasted categories of stimulus features and the amount of available
data to test the robustness of our findings.
% comparison to localizer experiment
We compare results of the primary contrast of each stimulus on the level of
individual subjects to results that we gained from a visual localizer experiment
done with the same subjects \citep{sengupta2016extension}.
% summary of results main finding
Results of our whole-brain analyses suggest that the perception of verbal
``spatial information'' embedded in an auditory narrative contrasted with
``non-spatial information'' is correlated with increased activation in the
anterior PPA of both hemispheres.
% to do
Other possible ``honourable'' mentions (here? and in the following discussion?)
\begin{itemize}
    \item RSC
    \item what could be LOC / OPA
    \item AV; should (shortly) be discussed
    \item robustness (imo shortly discussed; it is about robustness not about
        how all contrasts are different in detail and how results differ in
        detail; yes, totally interesting but out of scope
    \item discuss negative contrasts?
\end{itemize}

@@

\todo[inline]{Following paragraph could pasted into method section to save space
here; a short interpretation is given there already; so methods/ results/
discussion are not absolutely separated there already}
% stimuli not designed for research purposes
The audio-description and the movie were not designed to be used in a BOLD fMRI
experiment but to entertain their audiences.
%
As a results, stimulus features that we annotated to create the regressors could
have been correlated leading to shared variance that lowers detection power.
% computing the correlations
Hence, we first tested for correlation of regressors within and across both
naturalistic stimuli (s. Figure \ref{fig:reg-corr})
% results of computing feature correlation
Results show no to minor correlations of regressors with regressors of the same
stimulus.
% encouraged by that we build contrasts (statement)
Thus, we felt encouraged to create traditional/canonical voxel-wise GLMs that
modeled and contrasted hemodynamic activity similarly to previous studies that
used conceptualized stimuli.

@@

\todo[inline]{I read Aziz again: visual localizer: radius of 16 mm around peak
    voxel in each hemisphere = PPA; sentence experiment: reduced activity only
    in left PPA, and only for famous places vs famous faces; I think they ran
    their f-test on the average of the PPA voxels! anyway: their analysis is
complicated, yet not sophisticated}

% AO stimulus
Group results of the AO stimulus' primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap that we gained from a
visual localizer experiment \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} who modeled events from on- to offset of
sentences (describing unknown and famous places and faces), we modeled events
from on- to offset of single words (that cue the listener about the missing
visual content).
% conclusion
\citep{aziz2008modulation} found significantly increased activity in only the
left PPA and only for sentences describing famous places compared to famous
faces. Contrary, our group results suggest that auditory spatial information
compared to non-spatial information correlates with bilaterally increased
activation in its anterior.\todo{nice! and\dots?}

% tasks in previous studies
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but epstein1998
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a (perceptual) judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Our paradigm still differs from \citep{epstein1998ppa} because the modeled
stimulus features were incidentally embedded in a continuous stream of auditory
information.
% concluding statement: kinda automatic process
The lack of a task suggests that verbal spatial information is processed in the
anterior PPA in an automatic fashion and does not necessarily rely on
deliberately paying attention to verbal spatial information.
%
Further, the incidential occurrence of modeled features prevents participants
from making assumptions about the investigated perceptual process by just being
exposed to the paradigm which mimics experiencing the world outside the lab more
closely.

% AV stimulus
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
overlap) with group ROI?}
% confound of higher perception
This larger extension, especially into the primary visual cortex, can be
attributed to the fact that we averaged the content of individual frames after a
cut and did not control for confounding features like depicted faces or
objects,and low-level visual features.
% cross-modal control purpose?
\todo[inline]{better frame that it is conceptual/cross-modal control; but what
do the results tell us? yes, it ``kinda works'' but \dots?}
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
results?}

@@

% why we did a couple of contrasts
For both stimuli we created several contrasts that varied the amount of
events available for the analysis and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show significant
bilateral clusters in the anterior part of the group PPA overlap.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but extending into more posterior brain regions.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust across contrasts and do not depend on the design of one specific
contrasts.

% but
Nevertheless, results also suggest that ``localization performance'' depends on
the amount of available data and how well the feature space is modeled.
% example
For example, contrast 8 of the AO stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a stimulus to be chosen may provide and how homogeneous the events to be
averaged might be.

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements[, or
memory].\todo{which kind of memory}
% AO: auditory cortices
Nevertheless, contrasts of the AO stimulus that compare verbal cues about the
change of a setting (\texttt{se\_new} or \texttt{se\_old}) to categories that do
not cue a change of a setting (contrasts 2, 3, 6, 7) show significant clusters
in (primary and secondary) auditory cortices.\todo{``poor job of nuisance
regressors?}
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.\todo{ouf\dots}
% possible reason
This could be attributed to a possible change of the soundscape when the
narrative switches to a new setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

% intro
Results of the AO contrasts consistently yielded significant clusters spatially
constrained to the anterior part of the PPA group overlap [and to the anterior
part of significant clusters of the AV contrasts].
% PPA might have submodules
Previous studies provide evidence that the posterior PPA (pPPA) and anterior PPA
(aPPA) show differences in both functional connectivity profiles and in response
to low- and high-level visual features.

% posterior connectivity
The pPPA is more strongly functionally connected to the occipital visual cortex
\citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% functionality
Moreover, the pPPA is functionally more responsive than the aPPA to low-level
features of scenes or (abstract) objects \citep{baldassano2013differential,
nasr2014thinking, rajimehr2011parahippocampal}.

% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
Moreover, the aPPA is functionally more responsive than pPPA to high-level
features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).

\todo[inline]{the mother of total confusion: Aminoff shifts the PPA along the
    anterior-poster axis depending on the publication; in Aminoff (2007, 2013):
    anterior PPA = spatial associations, region anterior to (!) PPA =
    non-spatial associations; in Aminoff (2015): posterior PPA = spatial
associations, anterior PPA = non-spatial associations; hence: complete bullshit;
ignore Aminoff (2015) due to various reasons}

@@

\begin{itemize}

\item Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene
Perception \item Dilks, Kanwisher (2013). The Occipital Place Area Is Causally
and Selectively Involved in Scene Perception \item Nasr (2011). Scene-selective
    cortical regions in human and nonhuman primates \item Dilks (2011).
    Mirror-image sensitivity and invariance in object \& scene processing \item
    MacEvoy and Epstein (2007). Position selectivity in scene- and
object-responsive \item Grill-Spector (2003). The neural basis of object
    perception \item Hasson (2003). Large-scale mirror-symmetry organization
    \item Nakamura (2000). Functional delineation of the human occipito-temporal
        areas \end{itemize}

@@
